Kindly Bent to Free Us

### 2020-06-03 kindly/extensions.tex
Address a few more comments.
Improve the comparison matrix.
algebraic datatypes

\begin{lstlisting}[numbers=none]
let a = &x in (f a; g (&!x))
\end{lstlisting}

This code pattern is dynamically safe because $a$ is not used after
the function call @f a@.
Non-lexical lifetimes (NLL) handle such a pattern by removing expressions
that do not mention $a$ from its region; in this example,  NLL removes
the last expression.
%
In \lang, regions are lexical and marked by the
expression $\region{b}{e}$.
During inference, kind constraints prevent escaping from
a region.

@@

\subsection{Capabilities and Identity}

@@

\begin{lstlisting}
type ('a : 'k) llist : lin = Nil | Cons of ('a * 'a llist)
\end{lstlisting}

This extension is implemented in our prototype.

>>>>

\begin{lstlisting}[numbers=none]
let a = &x in (f a; g &!x)
\end{lstlisting}

This code pattern is dynamically safe because $a$ is not used after
the function call @f a@.
Here, this can be made explicit by transforming
the code to @(let a = &x in f a); g &!x@. However, this is not possible
in programs with branches who uses different dynamic patterns.
Non-lexical lifetimes (NLL) handle such a pattern by removing expressions
that do not mention $a$ from its region; in this example,  NLL removes
the last expression.
%
In \lang, regions are lexical and marked by the
expression $\region{b}{e}$.
During inference, kind constraints prevent escaping from
a region.

@@

\subsection{Capabilities and Identity}
\label{identity}

@@

\begin{lstlisting}[numbers=none]
type ('a : 'k) llist : lin = Nil | Cons of ('a * 'a llist)
\end{lstlisting}

Our prototype implements non-recursive algebraic datatypes with
pattern matching.
